ESI for "Probabilistic determination of the effect of a deep eutectic solvent on the structure of lipid monolayers"

### 2018-06-27 reports/esi.tex
Second draft now with neutrons

The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg5}
\end{figure}

>>>>

The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the X-ray reflectometry models are given in Figures \ref{fig:dlpc4}-\ref{fig:dmpg5}. The two-dimensional probability distribution functions (PDFs) for all parameters and all lipids from the neutron reflectometry models are given in Figures \ref{fig:dmpc3_1}-\ref{fig:dppc3_2}.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dlpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DLPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dlpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc5}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg4_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at the second-highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg4}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPG X-ray reflectometry data at the highest concentration. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpg5}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc3_neutron_corner1}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC/h-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc3_1}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dmpc3_neutron_corner2}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DMPC/hd-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dmpc3_2}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc3_neutron_corner1}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC/h-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc3_1}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.50\textwidth]{figures/dppc3_neutron_corner2}
	\caption{The multi-parameter PDFs for the chemically-relevant model of DPPC/hd-DES neutron reflectometry data. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:dppc3_2}
\end{figure}
